CO($J$ = 3 $\rightarrow$ 2) observation in a strongly lensed type-2 quasar host SMG at $z$ = 2.221 with continuum detection in the foreground lensing FR-II radio galaxy at $z$ = 0.685

### 2015-06-24 skeleton.tex
Need to fix from SED radio section

\begin{abstract}
We report the detection of CO($J$ = 3 $\rightarrow$ 2) line emission in SMM J0939+8315 ($z$ = 2.221), a
strongly lensed high-redshift submillimeter galaxy (SMG) hosting a type-2 quasar using
the Combined Array for Research in Millimeter-wave Astronomy (CARMA). This lensing system consists of a
foreground FR-II radio galaxy and a companion galaxy at $z$ = 0.685. We perform lens modeling on the Submillimeter Array 
(SMA) 1 mm dust continuum, resulting a
lensing magnification factor of $\mu=$9.7 $\pm$ 1.4. This allows us to place constraints on the intrinsic properties
of the cold gas and dust in the interstellar medium (ISM) of the background quasar host SMG. Prior to correcting for lensing 
amplification, we measure the
velocity-integrated CO($J$ = 3 $\rightarrow$ 2) line intensity of $I_{\rm CO(3-2)}$ = (14.6 $\pm$ 0.9) Jy km s$^{-1}$,
corresponding to a lensing-corrected CO($J$ = 1 $\rightarrow$ 0) line luminosity of $L^{\prime}_{\rm CO(1-0)}$ = (4.1 $\pm$ 
0.9) $\times$ 10$^{10}$ K km s$^{-1}$ pc$^2$. This
translates to a molecular gas mass of $M_{\rm gas}$ = 3.3 $\times$ 10$^{10}M_\odot$, assuming a conversion
factor of $\alpha_{\rm CO}$=0.8 $M_{\odot}$ (K km s$^{-1}$ pc$^2$)$^{-1}$. We report marginally resolved continuum 
emission from the foreground radio galaxy 3C220.3 with peak flux density of $S_\nu$ = 5.56 $\pm$ 0.54 mJy
 at 104 GHz (1.7 mm rest-frame), allowing us to put constraints on the spectral energy distribution (SED) of this galaxy. We 
fit
 both an optically thick and optically thin modified blackbody models to the SED of the SMG using existing
infrared photometric data. Our SED fitting favours an optically thick model, yielding dust mass of $M_{\rm
dust}$ = 50.5$^{20.4}_{-20.2}$ $\times$ 10$^8 M_{\odot}$, and total infrared (IR) luminosity of $L$ = 88.5$^{+2.6}
_{-2.6}\times$10$^{12}L_{\odot}$, prior to lensing correction. We conclude that the properties (e.g., gas mass, gas mass 
fraction, SFR) of the molecular gas reservoir in SMM
J0939+8315 based on our CO($J$ = 3 $\rightarrow$ 2) observation is similar to other high redshift
SMGs. \\
NEED TO  FIX: 
report SFR, gas-to-dust ratio..
The dust blah, and other properties similar to existing blah (M gas is similar to HLSW-01), This study blah?. the
population.\end{abstract}
\keywords{galaxies: formation --- galaxies: high-redshift --- submillimeter: galaxies}

@@

%% ok down
One of such lens system has a peculiar configuration consisting of a SMG (SMM J0939+8315; SMM J0939 hereafter) hosting a 
type-2 quasar host at $z$ = 2.221 being strongly lensed by a double-lobed FR-II radio galaxy (3C220.3) which has a 
companion galaxy B at $z$ = 0.685. The two lenses are separated by 1\farcs5. The redshift of the background SMG has 
been measured through the detection of CIV 1459\AA\
 and HeII 1640\AA\
line emissions \citep{Haas14}, these line detections provide conceiving evidence of AGN activity in the SMG, as well as the 
existence of a type-2 quasar.
The background SMG has a lensing-magnified flux density of $F_{\rm 250\mu m}$ = 440 $\pm$ 15 mJy, which is one of 
the
brightest known even among lensed
SMGs.

@@

%Deconvolution size bigger than expected (if just radio core):
%1) phase error that wasn't well calibrated (~30/360 $\times$\appox 16") ~ 1-2"
%2) low SNR giving rise to fitting error ~ 4" from `imfit`
%3) PA beam align with RG (radio galaxy) orientation
Averaging over all the line-free channels, we detect the continuum with peak flux density of S$_\nu$ = 5.56 $\pm$ 0.54 
mJy beam$^{-1}$ at an averaged frequency of $\nu_{cont}$ = 104.2106 GHz (2.877 mm) in the observed-frame, corresponding to $\sim$2.79 mm at $z$ = 0.658. In this lens system, the 
foreground galaxy (3C220.3) is radio-loud, hence we expect the continuum to be dominated by the foreground galaxy. The 
deconvolved source size in the continuum image is 8\farcs72 $\pm$ 0\farcs69 $\times$ 3\farcs87 $\pm$ 1\farcs60, and the integrated flux density is 7.18 $\pm$ 0.69 mJy. 
In Figure \ref{fig:cont}, we show the new measurement of the continuum emission at 104 GHz overlaid on the VLA 9 GHz continuum measurement reported by \citet{Haas14}. The figure demonstrates that at the resolution of our observation, the continuum detection is marginally resolved, it is therefore plausible that both non-thermal and thermal emissions from the lobes and the radio core contribute to the integrated flux density this frequency.

@@

\subsection{New results: CO($J$ = 3 $\rightarrow$ 2) line emission}
We detect CO($J$ = 3 $\rightarrow$ 2) line emission toward the background SMG SMM J0939. We fit a four-parameter single-component Gaussian to the spectrum as shown in Figure \ref{fig:mom0}, yielding peak flux density of 19.9 $\pm
$ 2.2 mJy superimposed on a continuum level of 3.46 $\pm$ 0.40 mJy at the peak position of the CO emission; and FWHM of 541.65 $\pm$ 31.91 km s$^{-1}$. 
The spatial extent of the SMG is shown in the SMA 1 mm dust continuum in Figure \ref{fig:mom0}, the 
synthesized beam size of the SMA observation is 1\farcs42$ \times $1\farcs16, at P.A. -34.0\degr. As such, the CO($J$ = 3 $\rightarrow$ 2) detection in the SMG is spatially unresolved. We construct a velocity-integrated (0th moment) map of the CO($J$ = 3 $\rightarrow$ 2) 
emission using the continuum-subtracted data in the visibility plane, this results in velocity-integrated CO($J$ = 3 $\rightarrow$ 2) line flux of $S$ 14.6 $\pm$ 0.9 Jy km s$^{-1}$ over a velocity range of $\Delta$v = $\sim$378.1 km s$^{-1}$.

\begin{figure*}[tbph] 
\centering
\includegraphics[width=0.8\textwidth]{Figure/LinePanel}
\includegraphics[width=0.65\textwidth]{Figure/peak28_WiderSpectrum}
\caption{The central cross represents the coordinates for alignment between plots. The contour starts at $\pm$3$\sigma$, 
incrementing at
steps of $\pm$1$\sigma$. Top Left: Continuum-subtracted moment-0 map of the CO($J$ = 3 $\rightarrow$ 2) line emission in 
the background SMG with $\sigma$ = 0.7 Jy km s$^{-1}$ beam$^{-1}$. The angular resolution is 13$\farcs$57 $\times$ 
5\farcs77, as shown in the bottom left corner. 
Top Right: Contours of CO($J$ = 3 $\rightarrow$ 2) emission (red) overlaid on the SMA 1 mm dust continuum (green) with $
\sigma$ = 0.84 mJy beam$^{-1}$. The beam size of the SMA data is 1\farcs42$ \times $1\farcs16, P.A. -34\degr, as shown 
in the bottom left corner. From this image, it is apparent that the extent of the background SMG is smaller than the beam 
size of the CARMA observations, hence the CO($J$ = 3 $\rightarrow$ 2) line detection is spatially unresolved. Bottom: Solid black line shows the Gaussian fit to the CO ($J$ = 3 $\rightarrow$ 2) line profile. Yellow histogram shows the 
flux density as a function of velocity offset, where 0 km/s corresponds to $z$ = 2.221. 
\label{fig:mom0}}
\end{figure*}

\section{Analysis}
\subsection{Lens Modelling} \label{sec:Lens} %ok except table and errors
To study the intrinsic properties of the background galaxy, we determine the magnification factor by performing
lens modeling using the SMA 1 mm archival data of this system. The lens modeling is carried out in the visibility
(uv-) plane using the updated version\footnote{commit: 7aee6276} of the publicly available software {\sc uvmcmcfit}
(Bussmann et al., 2015). The code uses affine-invariant Markov chain Monte Carlo (MCMC) to sample the posterior
probability density function (PDF) of the model parameters. In our lens model, the surface mass densities of both
lenses are represented by singular isothermal ellipsoid (SIE) profiles, and the source is assumed to have an
elliptical Gaussian profile. The code does not include an external shear parameter. \newline
We fix the phase center to coordinates ($\alpha$, $\delta$) (J2000) = (144.84809\degr, 83.25725\degr), the
offset positions of the lenses and source are referenced to this phase center. The primary lens (3C220.3) is
described by 5 free parameters: the angular offset relative to
the chosen phase center in the image ($\Delta \alpha_{\rm
lens0}$ and $\Delta \delta_{\rm lens0}$), the angular Einstein radius ($\theta_{\rm E,0}$), the
axial ratio ($q_{\rm lens0}$), and the position angle ($\phi_{\rm lens0}$). The secondary lens (companion B) is
described by 3 free parameters: $\theta_{\rm E,1}$, $q_{\rm lens1}$, and $\phi_{\rm lens1}$. The angular offset
of the secondary
lens is sampled with respect to ($\Delta \alpha_{\rm lens0}$ and $\Delta \delta_{\rm lens0}$) of
the primary lens.
The source (SMM J0939+8315) is parameterized by
6 free parameters: the position of the source relative to the
primary lens ($\Delta \alpha_{\rm s}$ and $\Delta
\delta_{\rm s}$), the total intrinsic flux density ($S$), the
effective radius ($r_{\rm s} = \sqrt{a_{\rm s} b_{\rm s}}$), the axial
ratio ($q_{\rm s}$ =  $b_{\rm s}/a_{\rm s}$), and the position angle
($\phi_{\rm s}$).
The total number of free parameters is $N_{\rm free}$ = 14. The best-fit model is obtained by maximizing the
Gaussian likelihood function $ \mathcal{L} $ according to:
\begin{equation}
    \mathcal{L} = \sum_{u, v}\left( \frac{|V_{\rm data} - V_{\rm
    model}|^2}{\sigma^2} + {\rm log}(2 \pi \sigma^2) \right)
\end{equation}
\noindent where $\sigma$ is determined from the scatter in the visibilities within a
single spectral window (natural weighting).

@@

The resulting best-fit model as shown in Figure \ref{fig:lens} shows no significant bowls in the residual
image, and the knots (lensed emission) in the observed SMA data are well-reassembled with the best-fit model.
The best-fit model yields a magnification
factor of $\mu_{\rm 1mm}$ = 9.73 $\pm$ 1.38, this is consistent the reported value in Haas et al.
2014 within errors. The Einstein radii associated with the best-fit model for the two lenses are $\theta_{E}$ =
1.22 $\pm$ 0.01 (8.75 kpc at $z$ = 0.685) and $\theta_{E}$ = 0.73 $\pm$ 0.02 (5.23 kpc at $z$ = 0.685),
the corresponding masses within the Einstein radii are $M(\theta < \theta_{\rm E})$ = (4.90 $\pm$ 0.58) $\times$ 10$^{11}$ 
$M_{\odot}$ and $M(\theta < \theta_{\rm E})$ = (1.76 $\pm$ 0.33) $\times$ 10$^{11}$ $M_{\odot}$, respectively. All best-fit
parameters are listed in Table \ref{tab:lensParam}.
\input{table_lensParams}

\subsection{SED fitting} \label{sec:SED}
%Lensing system, both foreground and background objects contribute to the emission, especially at frequency near
%100 GHz.
\subsubsection{3C220.3}

We detect the radio continuum with peak flux density of S$_\nu$ = 5.56 $\pm$ 0.54 mJy at $\nu_{cont}$ = 104.2106 GHz 
(2.877 mm) in the observed-frame. In this lens system, the foreground galaxy (3C220.3) is a double-lobed FR-II radio galaxy, 
hence we expect the continuum to be dominated by synchrotron emission from the foreground galaxy. At this frequency, we 
expect the emission from the radio core to dominate our continuum detection; however, the integrated flux density is measured 
to be 7.18 $\pm$ 0.69 mJy. Considering the fact that the orientation of the synthesized beam aligns with the axis along the 
lobes of the foreground radio galaxy as shown in Figure \ref{fig:cont}, we interpret this difference between the peak flux 
density and the integrated flux density as the source (core and lobes) being partially resolved, i.e., the continuum detection 
includes non-thermal emission from the lobes. Besides, the contours of the 104 GHz continuum are
centered on the north lobe of the radio galaxy, this further supports our argument.
%% OK up

Considering the fact that the orientation of the synthesized beam aligns with 
the axis along the lobes of the foreground radio galaxy as shown in Figure \ref{fig:cont}, we interpret this difference between 
the peak flux density and the integrated flux density as the source (core and lobes) being partially resolved, i.e., the 
continuum detection includes non-thermal emission from the lobes.

Talk about the radio core:
\citet{Mullin06a} report null detection of the radio core with upper limit of blah mJy at 4.6 GHz, whereas \citet{Haas14} 
report a detection of the radio core of 0.8 mJy at 9 GHz. 
We fit a functional form for the radio lobe to NED data following Equation (1) by \citet{Cleary07a}, extrapolate to continuum 
frequency = blah mJy. which is consistent with our continuum measurement. BLLAHHHH

We estimated the radio core contribution at our continuum frequency by taking two FR-II galaxies from the
3C catalog that have measurements on the radio core.

%By calculating their core spectral index, we extrapolated the radio core emission of 3C220.3 to our continuum frequency to 
be blah mJy, implying the continuum is dominated by the radio lobe.

Therefore the X $\sigma$ detection of the partially resolved continuum emission from the foreground radio galaxy suggests a 
non-negligible contribution coming from the lobe emission, the peak flux density therefore does not corresponds to the core 
emission.

\begin{figure}[!tbph]
\centering
\includegraphics[width=0.5\textwidth]{Figure/3C220_3FullSED}
\caption{Figure shows the SED of 3C220.3 and SMM J0939+8315 including the new measurements presented in this paper. 
Black markers represent existing data of 3C220.3 (see table \ref{tab:SEDdataRadio}). Red markers at 104 GHz corresponds to 
our continuum measurements (integrated, peak, and difference). The dashed black line corresponds to the parabolic function we 
fit to the data associated with the radio galaxy following \citet{Cleary07a} and references therein. The dashed blue line and 
the dashed dot magenta line correspond to the best-fit SED of the background galaxy using an optically thick model, and an 
optically thin model, respectively. \label{fig:SED}}
\end{figure}

>>>>

\begin{abstract}
We report the detection of CO($J$ = 3 $\rightarrow$ 2) line emission in SMM J0939+8315 ($z$ = 2.221), a
strongly lensed high-redshift submillimeter galaxy (SMG) hosting a type-2 quasar using
the Combined Array for Research in Millimeter-wave Astronomy (CARMA). This lensing system consists of a
foreground radio galaxy and a companion galaxy at $z$ = 0.685. We perform lens modeling on the Submillimeter Array 
(SMA) 1 mm dust continuum, resulting a
lensing magnification factor of $\mu=$9.7 $\pm$ 1.4. This allows us to place constraints on the intrinsic properties
of the cold gas and dust in the interstellar medium (ISM) of the background quasar host SMG. Prior to correcting for lensing 
amplification, we measure the
velocity-integrated CO($J$ = 3 $\rightarrow$ 2) line intensity of $I_{\rm CO(3-2)}$ = (14.6 $\pm$ 0.9) Jy km s$^{-1}$,
corresponding to a lensing-corrected CO($J$ = 1 $\rightarrow$ 0) line luminosity of $L^{\prime}_{\rm CO(1-0)}$ = (4.1 $\pm$ 
0.9) $\times$ 10$^{10}$ K km s$^{-1}$ pc$^2$. This
translates to a molecular gas mass of $M_{\rm gas}$ = 3.3 $\times$ 10$^{10}M_\odot$, assuming a conversion
factor of $\alpha_{\rm CO}$=0.8 $M_{\odot}$ (K km s$^{-1}$ pc$^2$)$^{-1}$. We report marginally resolved continuum 
emission from the foreground radio galaxy 3C220.3 with peak flux density of $S_\nu$ = 5.56 $\pm$ 0.54 mJy
 at 104 GHz (1.7 mm rest-frame), allowing us to put constraints on the spectral energy distribution (SED) of this galaxy. We 
fit
 both an optically thick and optically thin modified blackbody models to the SED of the SMG using existing
infrared photometric data. Our SED fitting favours an optically thick model, yielding dust mass of $M_{\rm
dust}$ = 50.5$^{20.4}_{-20.2}$ $\times$ 10$^8 M_{\odot}$, and total infrared (IR) luminosity of $L$ = 88.5$^{+2.6}
_{-2.6}\times$10$^{12}L_{\odot}$, prior to lensing correction. We conclude that the properties (e.g., gas mass, gas mass 
fraction, SFR) of the molecular gas reservoir in SMM
J0939+8315 based on our CO($J$ = 3 $\rightarrow$ 2) observation is similar to other high redshift
SMGs. \\
NEED TO  FIX: 
report SFR, gas-to-dust ratio..
The dust blah, and other properties similar to existing blah (M gas is similar to HLSW-01), This study blah?. the
population.\end{abstract}
\keywords{galaxies: formation --- galaxies: high-redshift --- submillimeter: galaxies}

@@

%% ok down
One of such lens system has a peculiar configuration consisting of a SMG (SMM J0939+8315; SMM J0939 hereafter) hosting a 
type-2 quasar host at $z$ = 2.221 being strongly lensed by a double-lobed Fanaroff-Riley Class II (FR-II) \citep*{Fanaroff74} radio galaxy (3C220.3) which has a 
companion galaxy B at $z$ = 0.685. The two lenses are separated by 1\farcs5. The redshift of the background SMG has 
been measured through the detection of CIV 1459\AA\
 and HeII 1640\AA\
line emissions \citep{Haas14}, these line detections provide conceiving evidence of AGN activity in the SMG, as well as the 
existence of a type-2 quasar.
The background SMG has a lensing-magnified flux density of $F_{\rm 250\mu m}$ = 440 $\pm$ 15 mJy, which is one of 
the
brightest known even among lensed
SMGs.

@@

%Deconvolution size bigger than expected (if just radio core):
%1) phase error that wasn't well calibrated (~30/360 $\times$\appox 16") ~ 1-2"
%2) low SNR giving rise to fitting error ~ 4" from `imfit`
%3) PA beam align with RG (radio galaxy) orientation
Averaging over all the line-free channels, we detect the continuum with peak flux density of S$_\nu$ = 5.56 $\pm$ 0.54 
mJy beam$^{-1}$ at an averaged frequency of $\nu_{cont}$ = 104.2106 GHz (2.877 mm) in the observed-frame, corresponding to $\sim$2.79 mm at $z$ = 0.658. In this lens system, the 
foreground galaxy (3C220.3) is radio-loud, hence we expect the continuum to be dominated by the foreground galaxy. We use CASA's {\sc imfit} task to estimate the peak position of the continuum emission, the deconvolved source size is 8\farcs72 $\pm$ 0\farcs69 $\times$ 3\farcs87 $\pm$ 1\farcs60, and the integrated flux density is 7.18 $\pm$ 0.69 mJy. 
In Figure \ref{fig:cont}, we show the continuum emission at 104 GHz overlaid on the 9 GHz continuum measurement reported by \citet{Haas14}. The figure demonstrates that at the resolution of our observation, the continuum detection is marginally resolved, it is therefore plausible that both non-thermal and thermal emissions from the lobes and the radio core contribute to the integrated flux density in our measurement.

@@

\subsection{New results: CO($J$ = 3 $\rightarrow$ 2) line emission}
We detect CO($J$ = 3 $\rightarrow$ 2) line emission toward the background SMG SMM J0939. We fit a four-parameter single-component Gaussian to the spectrum as shown in Figure \ref{fig:mom0}, yielding peak flux density of 19.9 $\pm
$ 2.2 mJy superimposed on a continuum level of 3.46 $\pm$ 0.40 mJy at the peak position of the CO emission; and FWHM of 541.65 $\pm$ 31.91 km s$^{-1}$. 
The spatial extent of the SMG is shown in the SMA 1 mm dust continuum in Figure \ref{fig:mom0}, the 
synthesized beam size of the SMA observation is 1\farcs42$ \times $1\farcs16, at P.A. -34.0\degr. As such, the CO($J$ = 3 $\rightarrow$ 2) detection in the SMG is spatially unresolved. We construct a velocity-integrated (0th moment) map of the CO($J$ = 3 $\rightarrow$ 2) 
emission using the continuum-subtracted data in the visibility plane, this results in velocity-integrated CO($J$ = 3 $\rightarrow$ 2) line flux of $S$ = 14.6 $\pm$ 0.9 Jy km s$^{-1}$ over a velocity range of $\Delta$v = $\sim$378.1 km s$^{-1}$, the uncertainty does not include $\sim$ 15\% calibration uncertainty. We ignore the primary beam correction given that the source is close to the phase center, and that the source is unresolved (i.e., much smaller than the primary beam size).

\begin{figure*}[tbph] 
\centering
\includegraphics[width=0.8\textwidth]{Figure/LinePanel}
\includegraphics[width=0.65\textwidth]{Figure/peak28_WiderSpectrum}
\caption{The central cross represents the coordinates for alignment between plots. The contour starts at $\pm$3$\sigma$, 
incrementing at
steps of $\pm$1$\sigma$. Top Left: Continuum-subtracted moment-0 map of the CO($J$ = 3 $\rightarrow$ 2) line emission in 
the background SMG with $\sigma$ = 0.7 Jy km s$^{-1}$ beam$^{-1}$. The angular resolution is 13$\farcs$57 $\times$ 
5\farcs77, as shown in the bottom left corner. 
Top Right: Contours of CO($J$ = 3 $\rightarrow$ 2) emission (red) overlaid on the SMA 1 mm dust continuum (green) with $
\sigma$ = 0.84 mJy beam$^{-1}$. The beam size of the SMA data is 1\farcs42$ \times $1\farcs16, P.A. -34\degr, as shown 
in the bottom left corner. From this image, it is apparent that the extent of the background SMG is smaller than the beam 
size of the CARMA observations, hence the CO($J$ = 3 $\rightarrow$ 2) line detection is spatially unresolved. Bottom: 
The spectrum at the CO emission peak position with spectral resolution of $\Delta$v $\sim$29.1 km s$^{-1}$.
Solid black line shows the Gaussian fit to the CO ($J$ = 3 $\rightarrow$ 2) line profile. Yellow histogram shows the 
flux density as a function of velocity offset, where 0 km/s corresponds to $z$ = 2.221. \label{fig:mom0}}
\end{figure*}

\section{Analysis}
\subsection{Lens Modelling} \label{sec:Lens} 
To study the intrinsic properties of the background galaxy, we determine the magnification factor by performing
lens modeling using the SMA 1 mm archival data of this system. The lens modeling is carried out in the visibility
(uv-) plane using the updated version\footnote{commit: 7aee6276} of the publicly available software {\sc uvmcmcfit}
\citep{Bussmann15a}. The code uses affine-invariant Markov chain Monte Carlo (MCMC) to sample the posterior
probability density function (PDF) of the model parameters. In our lens model, the surface mass densities of both
lenses are represented by singular isothermal ellipsoid (SIE) profiles, and the source is assumed to have an
elliptical Gaussian profile. The code does not include an external shear parameter. \newline
We fix the phase center to coordinates ($\alpha$, $\delta$) (J2000) = (144.84809\degr, 83.25725\degr), the
offset positions of the lenses and source are referenced to this phase center. The primary lens (3C220.3) is
described by 5 free parameters: the angular offset relative to
the chosen phase center in the image ($\Delta \alpha_{\rm
lens0}$ and $\Delta \delta_{\rm lens0}$), the angular Einstein radius ($\theta_{\rm E,0}$), the
axial ratio ($q_{\rm lens0}$), and the position angle ($\phi_{\rm lens0}$). The secondary lens (companion B) is
described by 3 free parameters: $\theta_{\rm E,1}$, $q_{\rm lens1}$, and $\phi_{\rm lens1}$. The angular offset
of the secondary
lens is sampled with respect to ($\Delta \alpha_{\rm lens0}$ and $\Delta \delta_{\rm lens0}$) of
the primary lens.
The source (SMM J0939) is parameterized by
6 free parameters: the position of the source relative to the
primary lens ($\Delta \alpha_{\rm s}$ and $\Delta
\delta_{\rm s}$), the total intrinsic flux density ($S$), the
effective radius ($r_{\rm s} = \sqrt{a_{\rm s} b_{\rm s}}$), the axial
ratio ($q_{\rm s}$ =  $b_{\rm s}/a_{\rm s}$), and the position angle
($\phi_{\rm s}$).
The total number of free parameters is $N_{\rm free}$ = 14. The best-fit model is obtained by maximizing the
Gaussian likelihood function $ \mathcal{L} $ according to:
\begin{equation}
    \mathcal{L} = \sum_{u, v}\left( \frac{|V_{\rm data} - V_{\rm
    model}|^2}{\sigma^2} + {\rm log}(2 \pi \sigma^2) \right)
\end{equation}
\noindent where $\sigma$ is determined from the scatter in the visibilities within a
single spectral window (natural weighting).

@@

The resulting best-fit model as shown in Figure \ref{fig:lens} shows no significant bowls in the residual
image, and the knots (lensed emission) in the observed SMA data are well-reassembled with the best-fit model.
The best-fit model yields a magnification
factor of $\mu_{\rm 1mm}$ = 9.73 $\pm$ 1.38, this is consistent the value reported by \citet{Haas14} within errors. The Einstein radii associated with the best-fit model for the two lenses are $\theta_{E}$ =
1.22 $\pm$ 0.01 (8.75 kpc at $z$ = 0.685) and $\theta_{E}$ = 0.73 $\pm$ 0.02 (5.23 kpc at $z$ = 0.685),
the corresponding masses within the Einstein radii are $M(\theta < \theta_{\rm E})$ = (4.90 $\pm$ 0.58) $\times$ 10$^{11}$ 
$M_{\odot}$ and $M(\theta < \theta_{\rm E})$ = (1.76 $\pm$ 0.33) $\times$ 10$^{11}$ $M_{\odot}$, respectively. All best-fit
parameters are listed in Table \ref{tab:lensParam}.
\input{table_lensParams}

\subsection{SED fitting} \label{sec:SED}
\subsubsection{3C220.3}

We detect the radio continuum with peak flux density of S$_\nu$ = 5.56 $\pm$ 0.54 mJy at $\nu_{\rm cont}$ = 104.2106 GHz 
(2.877 mm) in the observed-frame. In this lens system, the foreground galaxy (3C220.3) is a double-lobed FR-II radio galaxy, 
hence we expect the continuum to be dominated by emissions from the foreground galaxy. At this frequency, previous studies have suggested that contributions from the radio core dominates over that from the radio lobes and jets (cite).

Talk about the radio core:
\citet{Mullin06a} report an upper limit on the radio core of blah mJy at 4.6 GHz, whereas \citet{Haas14} 
report a detection of the radio core of 0.8 mJy at 9 GHz. 
We fit a functional form for the radio lobe to NED data following Equation (1) by \citet{Cleary07a} and references therein:
\begin{equation}
\log F_{\nu}^{\mathrm lobe} (\nu) \propto - \beta\ (\log\ \nu - \log \nu_{t})^2  + \log (\exp({\frac{\nu}{\nu_c^{\mathrm lobe}}}))
\end{equation}
where $\beta$ is a parameter representing the bending of the parabola, $\nu_t$ is the frequency at which the optical depth of the synchrotron emitting plasma reaches unity, and $\nu_v^{\rm lobe}$ is the frequency corresponding to the cutoff energy of the lobe plasma energy distribution.
$\nu_t >$ 1 MHz, 30 GHz $< \nu_c^{\rm lobe}$ 3000 GHz.
, extrapolate to continuum 
frequency = blah mJy. which is consistent with our continuum measurement.

We estimated the radio core contribution at our continuum frequency by taking two FR-II galaxies from the
3C catalog that have measurements on the radio core. Shows at these frequencies, what the radio core contribution is like
 thus we 
expect the emission from the core component to dominate our continuum measurement; however, the integrated flux density is measured 
to be 7.18 $\pm$ 0.69 mJy. Since the orientation of the synthesized beam aligns with the axis along the 
lobes of the radio galaxy as shown in Figure \ref{fig:cont}, we interpret the difference in the peak flux 
density and the integrated flux density as the source (core and lobes) being partially resolved, i.e., the continuum detection 
includes emissions from the lobes. Furthermore, the contours of the 104 GHz continuum are
centered on the north lobe of the radio galaxy in the overlay image, this further supports our argument.

Therefore the 10$\sigma$ detection of the partially resolved continuum emission suggests a 
non-negligible contribution coming from the lobe emission, the peak flux density therefore does not corresponds to the core 
emission.

\input{table_SED}
The continuum data used in plotting the SED of 3C220.3 is listed in Table \ref{tab:SEDdataRadio}

\begin{figure}[!tbph]
\centering
\includegraphics[width=0.5\textwidth]{Figure/3C220_3FullSED}
\caption{Figure shows the SED of 3C220.3 and SMM J0939 including the new measurements presented in this paper. 
Black markers represent existing data of 3C220.3 (see table \ref{tab:SEDdataRadio}). Red markers at 104 GHz corresponds to 
our continuum measurements (integrated, peak, and difference). The dashed black line corresponds to the parabolic function we 
fit to the data associated with the radio galaxy following \citet{Cleary07a} and references therein. The dashed blue line and 
the dashed dot magenta line correspond to the best-fit SED of the background galaxy using an optically thick model, and an 
optically thin model, respectively. \label{fig:SED}}
\end{figure}

\subsubsection{SMM J0939+8315} 
\input{table_SEDphoto}
%burn-in phase 100, walkers 500, steps 500,
To constrain the dust and gas properties in the ISM of SMM J0939, we perform SED fitting based on the
photometric data obtained using the Spitzer Space Telescope and the {\it Herschel} Space Telescope, at wavelengths
between observed-frame 70 \micron-1000 \micron, and the SMA interferometric data at 1 mm (Table \ref{tab:SEDdataSMG}. We use the publicly
available software {\sc mbb\_emcee} to perform SED fitting, the code uses an affine-invariant Markov chain Monte
Carlo (MCMC) approach, the details are described by \citet{Riechers13a} and \citet{Dowell14a}. The
functional form of the fit comprises of a modified blackbody function with a power law S$_{\lambda} \propto \lambda^\alpha
$ attached to the blue
side.
We fit both an optically thick and optically thin model. In the optically thick case, the wavelength $
\lambda_0$ = $\frac{c}{\nu_0}$ is an additional parameter which represents where the optical
depth $\tau_{\nu}$ = ($\nu$/$\nu_0$)$^\beta$ reaches unity. Thus, the functional form of the modified blackbody
in the optically thick regime is as follows:
\begin{equation}
\rm S_{\lambda} \propto \frac{(1-exp^{-(\frac{\lambda_0 (1+z)}{\lambda})^{\beta}})(\frac{c}{\lambda})^3}
{exp^{\frac{hc}{\lambda\rm{kT/(1+z)} } }-1}
\end{equation}
and in the optically thin regime, the functional form reduces to:
\begin{equation}
\rm S_{\lambda} \propto \frac{(\frac{c}{\lambda})^{\beta+3}}{exp^{\frac{hc}{\lambda\rm{kT/(1+z)}}}-1}
\end{equation}
where T is the rest-frame characteristic cold dust temperature (fitting to the FIR part), $\lambda_0$ is rest-frame wavelength
where the optical depth reaches unity, $\beta$ is the dust emissivity (or spectral index of the dust extinction
curve), and $\alpha$ is the power law spectral index. The overall fit is normalized using the observed-frame 500
$\micron$ flux density, hence this becomes an additional parameter in the fit. In both models, we impose an upper limit on $
\lambda_0$ to 2000 \micron, and the observed-frame dust temperature $T_{\rm d}/(1+z)$ to 60 K. We fix the upper limit on 
$\beta$ to be 3.0 and 2.2 for the optically thin model and optically thick model, respectively.

\input{table_mbb}
The best-fit values in both regimes are listed in Table \ref{tab:mbb}. The best-fit solution of an optically thin
model corresponds to $\chi^2$ = 5.31 with 3 degrees of freedom, whereas that of an optically thick model
corresponds to $\chi^2$ = 2.25 with 2 degrees of freedom, suggesting a better fit than the optically thin
model. In the subsequent analysis, we employ the inferred values from the optically thick model.
The best-fit solution yields a far-infrared (FIR) luminosity of $L_{\rm FIR (42.5-122.5\micron)}$ = 53.33$^{+1.14}_{-1.13}\times$10$^{12}L_
\odot$, and a total infrared (IR) luminosity of $L_{\rm IR (8-1000 \micron)}$ = 88.52$^{+2.62}_{-2.63}\times$10$
^{12}L_{\odot}$. Assuming a dust absorption coefficient of $\kappa_{\nu}$ = 2.64 m$^2$ kg$^{-1}$ at 125.0 $
\micron$ \citep{Dunne03a}, we derive the dust mass using the following expression:
\begin{equation}
\mathrm{M_{\rm dust}} = S_{\nu} \times D_{L}^2 [(1 + z) \kappa_{\nu} B_{\nu}]^{-1} \times \tau_{\nu} [1-
\exp(-\tau_{\nu})]^{-1}
\end{equation}
where $S_{\nu}$ is the flux density, $D_{\rm L}$ is the luminosity distance, $\kappa_{\nu}$ is the dust
absorption coefficient, $\tau_{\nu}$ is the optical depth, and $B_{\nu}$ is the Planck function,
all quantities are expressed in the observed-frame. We find a dust mass of $M_{\rm dust}$ =
50.47$^{20.42}_{-20.15}\times$10$^8 M_{\odot}$. These values are based on SED fitting to the photometric data, i.e. prior
to lensing correction.
